Supplement to Automatic Matching of Bullet Lands

### 2016-01-05 imaging-supplement.Rnw
now without the plot

set.seed(20151201+i); i+1
rtrees3 <- randomForest(factor(match)~., data=subset(ballstats, !flagged)[,includesVar], ntree=300); rtrees3
ballstats$forest <- predict(rtrees3, newdata=ballstats, type="prob")[,2]
xtabs(~(forest>0.5)+match+insmall, data=ballstats[!ballstats$flagged,])
qplot(forest, data=subset(ballstats, !flagged), geom="jitter", y=match)
@
% 9/(10628+9)
% 18/(76+18)

>>>>

set.seed(20151201+i); i+1
rtrees3 <- randomForest(factor(match)~., data=subset(ballstats, !flagged)[,includesVar], ntree=300); rtrees3
ballstats$forest <- predict(rtrees3, newdata=ballstats, type="prob")[,2]
#xtabs(~(forest>0.5)+match+insmall, data=ballstats[!ballstats$flagged,])
#qplot(forest, data=subset(ballstats, !flagged), geom="jitter", y=match)
@
% 9/(10628+9)
% 18/(76+18)
